---
title: "Partisan Lean"
date : "11/8/2022"
author: "Tamya Davidson"
subtitle: "Analyzing Partisan Lean in States"
format: html
editor: visual
execute:
  echo: true
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(lubridate)
library(readxl)
library(readr)


```

# Introduction

The data were taken from FiveThirtyEight.com 's GitHub repository with the goal of analyzing political lean between Congressional districts and States within the United States. According to FiveThirtyEight, "Partisan lean is the average difference between how a state or district votes and how the country votes overall, with 2016 presidential election results weighted 50 percent, 2012 presidential election results weighted 25 percent and results from elections for the state legislature weighted 25 percent.". The purpose of this project is to analyze how political lean has changed from 2018 to 2022 and use this to potentially predict results for the 2022 midterm elections. This analysis is being conducted after the 2022 Midterm election so towards the end of the project predicted results will be compared to actual results. The predicted results were not influenced by the actual results as the predictions will be made only using regression models and all changes made to the code will be present in the GitHub repository for clarity and transparency.

# Data Cleaning

```{r}
states_2018<- read_csv("partisan-lean/2018/fivethirtyeight_partisan_lean_STATES.csv")
districts_2018 <- read_csv("partisan-lean/2018/fivethirtyeight_partisan_lean_DISTRICTS.csv")
states_2020 <- read_csv("partisan-lean/2020/fivethirtyeight_partisan_lean_STATES.csv")
districts_2020 <- read_csv("partisan-lean/2020/fivethirtyeight_partisan_lean_DISTRICTS.csv")
states_2021 <- read_csv("partisan-lean/2021/fivethirtyeight_partisan_lean_STATES.csv")
districts_2021 <- read_csv("partisan-lean/2021/fivethirtyeight_partisan_lean_DISTRICTS.csv")
states_2022 <- read_csv("partisan-lean/fivethirtyeight_partisan_lean_STATES.csv")
districts_2022 <- read_csv("partisan-lean/fivethirtyeight_partisan_lean_DISTRICTS.csv")
```

# Methodology
